\textsf{Are frontier models superhuman chemists?}

### 2024-03-20 src/tex/appendix.tex
use nice fonts if they are available

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic_tiny.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of peaks in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic_tiny}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \label{fig:human_timing}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \label{fig:experience_vs_correctness}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in number of years since the first university-level chemistry course) of the human scorers was not significantly correlated with the correctness of their answers.}
\end{figure}

@@

\begin{figure} 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The barplots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

>>>>

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/performance_per_topic_tiny.pdf}
%     \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
%         We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of peaks in an \gls{nmr} spectrum.
%     }
%     \label{fig:performance_per_topic_tiny}
%     \script{analyze_performance_per_source.py}
% \end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \label{fig:human_timing}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \label{fig:experience_vs_correctness}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in number of years since the first university-level chemistry course) of the human scorers was not significantly correlated with the correctness of their answers.}
\end{figure}

@@

\begin{figure}[htb] 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The barplots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}
